### 2018-12-12 Sections/network_topologies.tex
Started QM section

@@

\subsection{Point-to-point} \index{Point-to-point (P2P)!Topologies}

@@

@@

\subsection{Complete} \index{Complete topologies}

@@

\subsection{Lattice} \index{Lattice!Topologies}

@@

\subsection{Tree} \label{sec:tree_graph} \index{Tree topologies}

@@

\subsection{Random}\index{Random!Topologies}

@@

>>>>

A summary of the mathematical characteristics of the topologies presented is shown in Table.~\ref{tab:net_top_sum}.\comment{Finish this text - expand on why these properties matter}

\startnormtable
\begin{table*}[!htbp]
	\begin{tabular}{|c|c|c|c|}
		\hline
  		Topology & Vertices ($|V|$) & Edges ($|E|$) & Diameter ($d$) \\
      	\hline
      	\hline
      	Point-to-point & $2$ & $1$ & $1$ \\
      	Linear & $|V|$ & \mbox{$O(|V|)$} & \mbox{$O(|V|)$} \\
      	Complete & $|V|$ & \mbox{$O(|V|^2)$} & $1$ \\
      	Lattice & $mn$ & \mbox{$O(mn)$} & \mbox{$O(m+n)$} \\
      	Tree & $|V|$ & \mbox{$O(|V|)$} & \mbox{$O(\log |V|)$} \\
      	Percolation & \mbox{$O(p_\mathrm{vertex}\cdot |V|)$} & \mbox{$O(p_\mathrm{edge}\cdot |E|)$} & variable \\
      	Random & \mbox{$O(p_\mathrm{vertex}\cdot |V|)$} & \mbox{$O(p_\mathrm{edge}\cdot |V|^2)$} & variable \\
      	Scale-free & $|V|$ & $|E|$ & \mbox{$O(\log\log |V|)$}\\
      	\hline
	\end{tabular}
	\captionspacetab \caption{Summary of the mathematical characteristics of different network topologies.} \label{tab:net_top_sum}
\end{table*}
\startalgtable

@@

\subsection{Point-to-point} \index{Point-to-point (P2P)!Topologies}\label{sec:P2P_topol}

@@

%
% Linear
%

\subsection{Linear}\index{Linear topologies}\label{sec:linear_topol}

\comment{To do}

@@

\subsection{Complete}\label{sec:complete_topol} \index{Complete topologies}

@@

\subsection{Lattice}\label{sec:lattice_topol} \index{Lattice!Topologies}

@@

\subsection{Tree}\label{sec:tree_topol} \label{sec:tree_graph} \index{Tree topologies}

@@

\subsection{Random}\label{sec:rand_topol}\index{Random!Topologies}

@@

\comment{Show average edge and vertex numbers}
